Figures for 3-D printed oxygen devices

### 2015-04-13 publishing/latex/paper.tex
added citation for sensor fab

Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate. 
The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, as well as bubble formation in the culture media.
The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports.
The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather then room air.
In this way, the pressure and therefore flow rate is equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.

Initially the inlets are fed with a 5\% \ce{CO2}, bal. air tank until the intensity stabilized.
The inlets are then switched to the control gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
Intensity measurements are then taken every five minutes for six hours.
All gas tanks used in the oxygen characterization were 5\% \ce{CO2} in addition to the desired gas mix in anticipation of cell culture experiments as \ce{CO2} can alter the fluorescence of the PtOEPK.
The this entire procedure was repeated three times for and sample size of three.

>>>>

Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate.
Senors were prepared as discussed previously \cite{Sinkala2010}. 
Briefly, polystyrene is dissolved in toluene to form a solution to which PtOEPK is mixed in before spinning coating to a thin layer and allowing the toluene to evaporate.
The intensity of the sensor was measured with via florescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).

Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, as well as bubble formation in the culture media.
The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports.
The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather then room air due to the open connection.
In this way, the pressure and therefore flow rate is equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.

Initially the inlets are fed with a 5\% \ce{CO2}, balanced air tank until the intensity stabilized.
The inlets are then switched to the control gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
Intensity measurements are then taken every five minutes for six hours.
All gas tanks used in the oxygen characterization were 5\% \ce{CO2} in addition to the desired gas mix in anticipation of cell culture experiments as \ce{CO2} can alter the fluorescence of the PtOEPK.
The this entire procedure was repeated three times for and sample size of three.
